Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-24 Response/Response 3/reviewer_response.tex

	\title{Reviewers Comments \& Authors Replies}

	\date{}
	\maketitle

	\begin{tabular}{p{1.25in}p{4.25in}}
		\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
		\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
		\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
	\end{tabular}

	\vspace{0.35in}
	The authors are grateful to the associate editor for giving us an additional opportunity to revise and correct our convergence analysis. In this regard, we would like to give a special thank to Review 3 who pointed out the issues with our convergence analysis of the proposed solutions. In this revision, we have mainly focused on providing a more mathematically rigorous  proof of the convergence analysis of the proposed iterative algorithms.
	%\input{additions}
	Towards this end the following changes have been made to the revised manuscript.
	\begin{enumerate}
		\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulated point (i.e., a limit point) is a stationary point. The proof is essentially based on the convergence of a subsequence of iterates. We have rewritten Appendix A-D according to these changes. In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})). Using this index \eqn{t}, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving convex subproblem (48) at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration. Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.		
		\item We have updated the convergence of distributed algorithms in a similar way.
	\end{enumerate}

### 2015-11-25 Response/Response 3/response-3.tex

\begin{enumerate}

	\item \reviewF{When discussing the convergence of the \ac{SCA} algorithm (Appendix A-C), the authors claim that the \ac{SCA} algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique. However, this is in general not enough to guarantee the convergence of the whole sequence. Instead, one can only claim that every limit point of the whole sequence is a stationary point, or globally optimal solution if the problem is convex. As an example, simply consider the gradient projection algorithm, where each subproblem is strongly convex and the objective function  is strictly decreasing but the whole sequence may not converge. The authors are referred to Bertsekas'  book: Nonlinear Programming.}

	\vspace{1eM}
	\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent. Based on the reviewer's reference to the gradient projection algorithm in Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous. We apologize for our emphasis on the convergence of iterates in our previous manuscript. As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements. 
	\begin{itemize}
		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can claim that there exist at least one subsequence of original sequence that converges to a limit point of original sequence.
		\item Using a convergent subsequence of original sequence of iterates, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
	\end{itemize}

@@

	We have made changes in Appendices A-C and A-D to address the concerns raised by the reviewer.

	\vspace{1eM}	
	\item \reviewF{Even under the assumption that the inner loop SCA converges, there are doubts with respect to the convergence of the alternating optimization algorithm described by (54). The authors cite [27] to justify convergence, but it is not straightforward to claim that the algorithmic model considered in this manuscript is the same as in [27]. More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D). In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{\mbf{x}} are updated simultaneously, based on \eqn{\sol{t}}. But in the authors' model, the update of \eqn{\mbf{x}} is performed in two phases: in the first phase, only the elements of \eqn{\mbf{m}} and \eqn{\mbf{\gamma}} in \eqn{\mbf{x}} are updated based on \eqn{\sol{t}}. In the second phase, the remaining elements of \eqn{\mbf{x}} are updated, i.e. \eqn{\mbf{w}} and \eqn{\mbf{\gamma}}, based on both \eqn{\sol{t}} and the elements that have been updated in the first phase. This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted. Due to the open concerns after several revision rounds, it is recommended to reject the paper.}

	\vspace{1eM}
	\underline{\textbf{Response:}} We understand the reviewer's concern on using reference [R1] to our problem involving both \ac{SCA} and \ac{AO} updates. In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use reference [R1] directly as suggested by the reviewer. Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.

	\begin{itemize}
		\item We refer to [R2] for a similar usage of reference [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem. The reference [R1] used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables. It has been discussed comprehensively in [R2, Appendices I and II]. In particular, the discussion on referring \ac{AO} as two sub-algorithms is presented in [R2, Appendix I-F].
		\item However, we apologize for the incomplete usage of [R1, Theorem 3.1] in our previous manuscript to claim the convergence of beamformer iterates. In [R1, Theorem. 3.1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
		\item Therefore, our previous statement claiming guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
		\item A similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is presented in [R1, Section 4] under restrictive mapping title. Therefore, even if we use the discussions from reference [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
	\end{itemize}

	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates. We have revised our statement as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.

### 2015-11-25 Response/Response 3/reviewer_response.tex

	\title{Reviewers Comments \& Authors Replies}

	\date{}
	\maketitle

	\begin{tabular}{p{1.25in}p{4.25in}}
		\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
		\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
		\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
	\end{tabular}

	\vspace{0.35in}
	The authors are grateful to the associate editor for giving us an additional opportunity to revise and correct our convergence analysis. In this regard, we would like to give a special thank to Review 3 who pointed out the issues with our convergence analysis of the proposed solutions. In this revision, we have mainly focused on providing a more mathematically rigorous  proof of the convergence analysis of the proposed iterative algorithms.
	%\input{additions}
	Towards this end the following changes have been made to the revised manuscript.
	\begin{enumerate}
		\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulation point (i.e., limit point) is a stationary point. The proof is essentially based on the convergence of a subsequence of iterates. We have rewritten Appendix A-D according to these changes. In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})). Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence of minimizers obtained at each iteration. With these notations, we have revised our convergence discussions in Appendices A-C and A-D.		
		\item We have updated the convergence of distributed algorithms in a similar way.
	\end{enumerate}

	We have  also revised some parts of text to support the changes mentioned above and to further improve the readability. Specifically, the following parts of the revision have been rewritten.
	\begin{itemize}
		\item Page 6, paragraph after (28): We have elaborated the discussions on showing that the feasible set is bounded.
		\item Page 8, last paragraph in Section IV-B: We have highlighted the conditions under which the overall objective sequence generated by the distributed methods will converge.
		\item Last sentence after (51) on page 14: We have emphasized the convergence of objective sequence only in each \ac{AO} step and not the iterates. 
		\item Last sentence after (60) on page 15: We have rewritten the convergence claim on the sequence of iterates generated by the Algorithm 2 similar to that of centralized method.
	\end{itemize}

### 2015-11-25 Report/convergence_centralized.tex
finalized so far

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the variables that are fixed. Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained on the \eqn{\ith{(k-1)}} \ac{SCA} step of \ac{AO} update instant \eqn{i}. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on the transmit precoders by the constraints \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.

The minimum value of the norm function present in the objective is \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all exponents used in \eqn{\ell_q} norm, therefore, it is bounded from below. Moreover, by the fact that the feasible set is compact, the objective function is Lipschitz continuous, and therefore bounded from above as well.

@@

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} update \cite{scutari2010convex}. \reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We now discuss the convergence properties of the sequence of iterates generated by the proposed algorithm. For convenience, let us consider a unified superscript index \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})). Using this, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
%Furthermore, we introduce variable \eqn{\ma^{t}} to denote a vector formed by stacking solution obtained at \eqn{\ith{t}} iteration, \textit{i.e.}, \eqn{\mat{t} = \mbf{z}^{(i)}_k}, the respective iterate.

The objective sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, the convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, since the feasible set is compact, the sequence \eqn{\{\ma^t\}} is bounded. Therefore, the sequence \eqn{\{\ma^t\}} has at least one limit point, say \eqn{\bar{\mbf{x}}}, such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\mbf{x}}} \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.

Before proceeding further, we also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that the original objective function in \eqref{orig_obj} also decreases at each iteration. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Since \eqn{\|\mat{} - \mat{t}\|^2} is the proximal term in \eqref{mod_obj} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|^2
\end{equation}
where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop. A.3]{bertsekas1999nonlinear}.

Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between gradients of subproblems \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}. In order to ensure \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the centralized method in Algorithm \ref{algo-1} by using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems \eqref{eqn-9} and \eqref{eqn-mse-2} is regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where vector \eqn{\mbf{z}} is formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the fixed variables. Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be a stacked vector of solution obtained at the \eqn{\ith{(k-1)}} \ac{SCA} step in \ac{AO} iteration \eqn{i}. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f(\mbf{z})} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f(\mbf{z})}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible set of \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders, given by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.%\footnote{The feasible set in each iteration is bounded due to the proximal operator in \eqref{mod_obj} as \eqn{\{\mbf{z} | f(\mbf{z}) \leq f(\mbf{z}_k^{(i)})\}}, therefore, the sequence \eqn{\{\mbf{z}_k^{(i)}\}} is bounded.}

Since the norm function present in the objective satisfies \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all \eqn{q} used in \eqn{\ell_q} norm, it is bounded from below. Moreover, due to the compactness of the feasible set, it is bounded from above as well. In addition, the objective function satisfies Lipschitz continuity, since the feasible set is compact.

@@

\begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub \allowdisplaybreaks

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} update \cite{scutari2010convex}. \reviewF{Since the objective is decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be a stacked vector of the solution obtained upon objective convergence in the \eqn{\ith{i}} \ac{AO} update.}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We now discuss the convergence properties of the sequence of iterates. For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step \eqn{(k,i)}). Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence of minimizers obtained at each iteration.

Note that the objective sequence \eqn{\{f(\ma^t)\}} is bounded and nonincreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, we can ensure the convergence of \eqn{\{f(\ma^t)\}}. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded, and therefore the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Thus, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.

Before proceeding further, we also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that the original objective function in \eqref{orig_obj} also decreases at each iteration. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Since \eqn{\|\mat{} - \mat{t}\|^2} is the proximal term in \eqref{mod_obj} at iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|^2
\end{equation}
where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Thus, by extending \eqref{mcity_origfunc} for each update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop. A.3]{bertsekas1999nonlinear}.

Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}. In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

### 2015-11-25 Report/dual_approach.tex
finalized so far

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing at every \ac{SCA} step. We recall that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

>>>>

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing at every \ac{SCA} step. We recall that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-25 Report/mse_formulation.tex
finalized so far

In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. By using the above assumptions, convergence analysis for the centralized problem is discussed in Appendix \ref{sec-3.5}.}

>>>>

In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. By using the above assumptions, convergence analysis for the centralized problem is discussed in Appendix \ref{sec-3.5}.}
